\section*{Executive Summary}

The C3S311a Lot2 (Global Land and Marine Observations Database) service is concerned with the provision of globally available land and marine surface meteorological records. 
The service includes inventorying of, and brokering access to, data sources, their harmonization (via conversion to a Common Data Model, merging, and quality assurance) and their provision via the Copernicus Climate Change Service Data Store (CDS).

This marine user guide describes all relevant aspects of the marine data service necessary for a user to access and work with the marine data appropriately and with confidence. 
This document does not constitute a technical service document which instead is available separately. 
There is also an accompanying land user guide that describes the land data and its processing.

This is a living document which shall be subject to regular revision to reflect the status of the service at any given point in time. Releases of this document will always accompany new data releases. On an exceptional basis, as warranted, additional releases may occur to clarify issues raised by users or document important changes between releases such as any modification to the modalities of data access. Feedback on the adequacy and completeness of the document is welcomed at any time. Feedback should be provided via the C3S helpdesk facility to allow C3S tracking of user input. All such feedback shall be passed on in full to the service team for due consideration.

Former versions are archived and available upon request. The version history is given below:

\begin{table}[h]
\begin{tabular}{|p{0.15\linewidth}|p{0.15\linewidth}|p{0.65\linewidth}|}
\hline
\bfseries Version & \bfseries Release Date & \bfseries Release notes \\\hline
0.0	& 31/08/17	& Initial version consisting of section outlines and description of initial archiving material \\\hline
1.0	& 14/12/17	& Updates to reflect the status of the test release \\\hline
2.0	& 17/12/18	& Update to reflect status of beta release \\\hline
3.0	& 14/10/19	& Update for first data release \\\hline
4.0	& 21/07/20	& Update after second data release \\\hline
5.0 & 29/03/21  & Update after third data release \\\hline
6.0 & \today    & Update after fourth data release \\\hline
\end{tabular}
\end{table}
\FloatBarrier
